Episodic memory: mental time travel or a quantum `memory wave' function?

### 2019-01-07 main.tex
backing up progress on results section

To examine which specific events are described (during recall) as more similar than what their original experiences (as characterized by semantic feature vectors) would suggest, it can be helpful to examine individual recalls of particular events throughout the episode.  Figure~\ref{fig:reinstatement}B displays, for a representative example recalled moment, which other moments from the episode were described in a similar way by the participants when they recounted the episode later (black and colored lines), and which other moments in the episode were described in a similar way in moment-by-moment (non-recall) human annotations (gray line).  The example event explored in the figure comprises a scene where Sherlock Holmes and John Watson (main characters) are bantering, and then are interrupted when Sherlock realizes that another victim has been murdered.  The language used by human annotators describing the moment-by-moment contents of the scene used a similar mix of themes only for moments in the episode that were temporally proximal to the event in question (gray line).  However, the way participants \textit{described} what happened when they recounted the episode later revealed a much different pattern.  Specifically, their language mirrored that used when they were recalling other murders, and other moments when Holmes and Watson were bantering (Fig.~\ref{fig:reinstatment}C).  This suggests that these events were associated in participants' memories, perhaps contributing to the understanding that those events were linked in the episode's narrative.

@@

>>>>

To examine which specific events are described (during recall) as more similar than what their original experiences (as characterized by semantic feature vectors) would suggest, it can be helpful to examine individual recalls of particular events throughout the episode.  Figure~\ref{fig:reinstatement}B displays, for a representative example recalled moment, which other moments from the episode were described in a similar way by the participants when they recounted the episode later (black and colored lines), and which other moments in the episode were described in a similar way in moment-by-moment (non-recall) human annotations (gray line).  The example event explored in the figure comprises a scene where Sherlock Holmes and John Watson (main characters) are bantering, and then are interrupted when Sherlock realizes that another victim has been murdered.  The language used by human annotators describing the moment-by-moment contents of the scene used a similar mix of themes only for moments in the episode that were temporally proximal to the event in question (gray line).  However, the way participants \textit{described} what happened when they recounted the episode later revealed a much different pattern.  Specifically, their language mirrored that used when they were recalling other murders, and other moments when Sherlock and John were bantering (Fig.~\ref{fig:reinstatement}C).  Further, the way they described this example event did \textit{not} mirror the way they described other semantically (but not conceptually) related events, such as events involving unrelated violence, or Sherlock and John interacting with other characters.  Taken together, this suggests that these specific events were associated in participants' memories, perhaps contributing to (or reflecting) their understanding that those events were linked in the episode's narrative.

@@

A rich recall density function analogous to the one displayed in Figure~\ref{fig:reinstatement}B could, in principle, be characteristic of memory for \textit{any} past event or experience.  For example, the peaks of the function could provide insight into which events, from which moments along one's autobiographical timeline, were functionally associated in memory.  Nonetheless, a potential challenge to testing this hypothesis in the laboratory is that in most memory studies there is no particular reason for participants to functionally associate the stimuli-- there is no ``deeper narrative'' to make sense of.  However, random word list learning experiments might happen to contain (for a given list) semantically related words.  And indeed, a number of studies indicate that participants spontaneously form associations between semantically related words on random word lists, even when those related words are separated in time~\citep[e.g.,][]{WixtRohr94, MannKaha12, MannEtal12}.  This suggests that our memory systems pick up on statistical regularities, even in ostensibly ``random'' stimulus sequences, and that we leverage those regularities when we recall our past~\citep{PolyEtal09}.  Other work suggests that our memory systems may also leverage these regularities to parse our ongoing experiences into discrete events~\citep{SchaEtal13}.  Given this well-developed literature on random list learning studies indicates that our memory systems leverage ``accidental'' structure in random sequences, \textbf{JRM STOPPED HERE}. %is it "sufficient"?  pros and cons of lists vs. naturalistic...

key question is whether the additional
